Supplementary material for "Hack Weeks as a model for Data Science Education and Collaboration"

### 2018-04-12 results.tex
Additional figures for appendix, added table to results section, modified text

\begin{figure*}[h!]
%\begin{center}
%\begin{subfigure}[t]{\textwidth}
\centering
%\caption{}
\includegraphics[width=\textwidth]{f2.eps}
%\end{subfigure}
\caption{Post-workshop surveys from three hack weeks: participants in the 2016 astro-, geo- and neuro- hack weeks responded to questions assessing their experiences. For GHW and NHW, response rates were 100\%, with $N_{\mathrm{GHW}}= 83$ and $N_{\mathrm{NHW}} = 86$, respectively. At AHW, the combined response rate for both years was 76\%, or $N_{\mathrm{AHW}} = 72$ out of $94$ total attendees. We report here about results in three different domains: the development of technical skills (a -- e), collaboration and learning (f,g), and shifts in attitudes towards reproducibility and open science (h -- j)}
\label{fig:survey}
%\end{center}
\end{figure*}

@@

Focusing on the outcomes of astro-, geo- and neuro- hack weeks (AHW, GHW, NHW, respectively) from 2016 and 2017, we find that most participants self-report successful learning outcomes (AHW: 76\%, GHW: 89\%, NHW: 79\% for responses ``somewhat agree'', ``agree'' and ``strongly agree''; Figure \ref{fig:survey}, (a)).
The overwhelming majority of respondents at the hack weeks ($>95\%$ for all three events) believed that they learned things that improve their day-to-day research, and that attendance has made them a better scientist (Figure \ref{fig:survey}, (b, c) ).
%More specifically, we compared learning outcomes in data visualization (the only topic explicitly shared between all three hack weeks; Figure \ref{fig:survey}, (d, e). We asked participants to subjectively rate their knowledge before the hack week, and find skill levels to be broadly distributed. This is expected, given the goal of diversity during the selection stage. We find that most participants have positive learning outcomes at all three hack weeks for data visualization, but that outcomes vary strongly, as is expected, too, with a group that is this diverse. We also note that there might be systematic effects and biases due to the subjectivity of rating knowledge and learning outcomes.

The majority of participants felt that they built valuable connections to other researchers (Figure \ref{fig:survey}, (g)), especially at Neuro Hack Week, where more than 64\% of participants strongly agreed with this statement. 
Because peer learning is a major mode of knowledge transfer at hack weeks, we asked participants whether they taught other participants.
We find that again a majority agrees with this statement to some degree (AHW: 79\%, GHW: 69\%, NHW: 75\%; Figure \ref{fig:survey}, (f)), though responses are not as unequivocal as they are in some of the other categories.
Similarly to learning outcomes, this is expected given the range of skill levels at the workshops. It is notable, however, that we find no correlation between the response to this question and career stage for any of the events surveyed here. Participants at all career stages report similar engagement in teaching. This suggests there is some evidence for our hypothesis that compared to e.g.\ a traditional summer school, a hack week is less hierarchical and encourages lateral knowledge transfer between participants at different career stages. However, we note that the sample sizes per category are relatively small, and future work is needed to confirm this hypothesis. We similarly find no correlations with gender identity or race/ethnicity.

We find that the hack weeks have been largely successful at efforts to promote positive attitudes towards reproducibility and open science: at all three events, the majority reports that the hack week has made them more comfortable with open science  (GHW: 97\%; NHW: 95\%; AHW: 72\%). %at all three events, more than 85\% of all participants (AHW: 86\%, GHW: 94\%, NHW: 95\%; Figure \ref{fig:survey}, (h)) put code or data created at the hack week into a public repository, while a substantially smaller fraction of participants followed a regular practice of publishing code before the event (Figure \ref{fig:survey}, (i)).
%The overall behaviour hints at how general conventions and attitudes differ in different fields.
%Astronomy shows the largest degree of openness toward open science, whereas our results indicate that open science is still fairly uncommon in the geosciences, with neuroscience falling in between.
%Similar attitudes are reflected when asking whether the hack week has made participants more comfortable with open science (Figure \ref{fig:survey}, (j)): again, geoscience shows the large improvement with over 97\% agreeing with this statement to some degree, followed by neuroscience (95\%) and astronomy (72\%).
%Overall, our results indicate that hack weeks are effective at addressing persisting doubts about making research open and reproducible. 
While the focus on open science is not necessarily a required component of a hack week, it aligns naturally with many of the goals and values commonly promoted at hack weeks like open-source software and data sharing. In some fields, especially where ethical issues around data sharing and privacy are relevant, this might not be a desired focus of the hack week, or might be replaced or augmented by a discussion of ethical considerations.

>>>>

\begin{table*}
%\begin{table*}[hbtp]
%\renewcommand{\arraystretch}{1.3}
\footnotesize
\caption{}
\begin{threeparttable} 
\begin{tabularx}{18cm}{p{3.4cm}p{0.3cm}p{0.33cm}p{0.33cm}p{0.33cm}p{0.33cm}p{0.33cm}p{0.33cm}p{0.33cm}p{0.33cm}p{0.33cm}p{0.33cm}p{0.33cm}p{0.33cm}p{0.33cm}p{0.33cm}p{0.33cm}p{0.33cm}p{0.33cm}}
\toprule
\textbf{Question} & \multicolumn{6}{c}{\textbf{Astro Hack Week}} & \multicolumn{6}{c}{\textbf{GeoHackWeek}} & \multicolumn{6}{c}{\textbf{NeuroHackWeek}} \\ \midrule
 & $N$ & $\mathrm{dof}_{\chi^2}$ & $\chi^2$ & $p$ & $\mathrm{dof}_{\phi_c}$ & $\phi_c$ & $N$ & $\mathrm{dof}_{\chi^2}$ & $\chi^2$ & $p$ & $\mathrm{dof}_{\phi_c}$ & $\phi_c$ & $N$ & $\mathrm{dof}_{\chi^2}$ & $\chi^2$ & $p$ & $\mathrm{dof}_{\phi_c}$ & $\phi_c$ \\ \midrule
\multicolumn{16}{l}{\textbf{Comparison with career stage}}  \\ \midrule
New topics, tools, methods (a) & 61 & 10 & 5.64 & 0.85 & 1.93 & 0 & 36 & 6 & 2.51 & 0.87 & 1.88 & 0 & 41& 10 & 15.53 & 0.15 & 1.9 & 0.23 \\
Improvement of research (b) & 61 & 6 &  9.89 & 0.13 & 1.93 & 0.18 & 35 & 4 & 12.41 & 0.02 & 1.88 & 0.35 & 40 & 6 & 7.42 & 0.28 & 1.90 & 0.13 \\
Better science (c) & 59 & 6 & 3.79 & 0.70 & 1.93 & 0 & 35 & 4 & 10.61 & 0.03 & 1.88 & 0.31 & 40 & 4 &  5.06 & 0.29 & 1.90 & 0.11\\ 
Teaching (d) & 10 & 61 & 13.65 & 0.19 & 1.93 & 0.17 & 36 & 10 & 13.68 & 0.19 & 1.88 & 0.22 & 40 & 10 & 6.90 & 0.74 & 1.90 & 0 \\ \midrule
\multicolumn{16}{l}{\textbf{Gender Identity}} \\ \midrule
Improvement of research (b) & 60 & 3 & 2.08 & 0.56 & 0.98 & 0 & 35 & 2 & 5.26 & 0.07 & 0.97 & 0.30 & 40 & 3 & 7.62 & 0.05 & 0.97 & 0.34\\
Teaching (d) & 61 & 5 & 7.30 & 0.20 & 0.98 & 0.19 & 36 & 5 & 12.71 & 0.26 & 0.97 & 0.46 & 40 &5 & 3.17 & 0.67 & 0.97 & 0 \\
Connection building (e) & 61 & 4 & 3.70 & 0.45 & 0.98 & 0 & 36 & 3 & 5.89 & 0.12 & 0.97 & 0.28 & 41 & 3 & 4.42 & 0.22 & 0.98 & 0.18\\
Valued contributions (f) & 57 & 4 & 5.98 & 0.20 & 0.98 & 0.18 & 34 & 5 & 9.46 & 0.09 & 0.97 & 0.36 & 38 & 5 & 6.75 & 0.34 & 0.97 & 0.21 \\ \midrule
\multicolumn{16}{l}{\textbf{Racial/ethnic Identity}} \\ \midrule
Improvement of research (b)  & 59 & 3 & 0.97 & 0.81 & 0.98 & 0 & 34 &2 & 0.01 & 0.99 & 0.97 & 0 & 39 & 3 & 2.79 & 0.43 & 0.97 & 0 \\
Teaching (d) & 61 & 5 & 5.63 & 0.34 & 0.98 & 0.09 & 34 & 4 & 1.29 & 0.86 & 0.97 & 0 & 39 & 5 & 3.06 & 0.69 & 0.97 & 0 \\
Connection building (e) & 61 & 4 & 1.64 & 0.80 & 0.98 & 0 & 34 & 3 & 8.42 & 0.04 & 0.97 & 0.40 & 40 & 3 & 3.49 & 0.32 & 0.97 & 0.10 \\
Valued contributions (f) & 58 & 4 & 13.14 & 0.01 & 0.98 & 0.40 & 32 & 5 & 2.49 & 0.78 & 0.96 & 0 & 37 & 5 & 4.05 & 0.54 & 0.97 & 0 \\ 
\bottomrule
\end{tabularx}
   \begin{tablenotes}
      \item{Respondents to a post-event evaluation survey indicate their level of agreement on a six-point Likert-type scale to a range of statements (corresponding to Figure \ref{fig:survey}). Results are for hack weeks held in 2016 and 2017 for AHW and in 2016 for GHW and NHW, respectively. The number of respondents for each question is included in the table above. Additional figures showing the distributions of scores are available in the Appendix.}
\end{tablenotes}

\end{threeparttable}
\label{tab:priors}
%\end{table*}
\end{table*}

\begin{figure*}[h!]
%\begin{center}
%\begin{subfigure}[t]{\textwidth}
\centering
%\caption{}
\includegraphics[width=\textwidth]{f2.eps}
%\end{subfigure}
\caption{Post-workshop surveys from three hack weeks: participants in the 2016 astro-, geo- and neuro- hack weeks responded to questions assessing their experiences. For GHW and NHW, response rates were 100\%, with $N_{\mathrm{GHW}}= 83$ and $N_{\mathrm{NHW}} = 86$, respectively. At AHW, the combined response rate for both years was 76\%, or $N_{\mathrm{AHW}} = 72$ out of $94$ total attendees. We report here about results in three different domains: the development of technical skills (a -- c), collaboration and teaching (d -- f), and shifts in attitudes towards reproducibility and open science (g, h).}
\label{fig:survey}
%\end{center}
\end{figure*}

@@

Focusing on the outcomes of astro-, geo- and neuro- hack weeks (AHW, GHW, NHW, respectively) from 2016 and 2017, we find that most participants self-report successful learning outcomes (AHW: 76\%, GHW: 89\%, NHW: 79\% for responses ``somewhat agree'', ``agree'' and ``strongly agree''; Figure \ref{fig:survey}, (a)).
The overwhelming majority of respondents at the hack weeks ($>95\%$ for all three events) believed that they learned things that improve their day-to-day research, and that attendance has made them a better scientist (Figure \ref{fig:survey}, (b, c)).
%More specifically, we compared learning outcomes in data visualization (the only topic explicitly shared between all three hack weeks; Figure \ref{fig:survey}, (d, e). We asked participants to subjectively rate their knowledge before the hack week, and find skill levels to be broadly distributed. This is expected, given the goal of diversity during the selection stage. We find that most participants have positive learning outcomes at all three hack weeks for data visualization, but that outcomes vary strongly, as is expected, too, with a group that is this diverse. We also note that there might be systematic effects and biases due to the subjectivity of rating knowledge and learning outcomes.

Because peer learning is a major mode of knowledge transfer at hack weeks, we asked participants whether they taught other participants.
We find that again a majority agrees with this statement to some degree (AHW: 79\%, GHW: 69\%, NHW: 75\%; Figure \ref{fig:survey}, (d)), though responses are not as unequivocal as they are in some of the other categories.
The majority of participants felt that they built valuable connections to other researchers (Figure \ref{fig:survey}, (e)), especially at Neuro Hack Week, where more than 64\% of participants strongly agreed with this statement.

Given the broad diversity in skills and backgrounds of participants admitted to our hack weeks, a dependence of learning outcomes and teaching on career stage is plausible. At the same time, we put forth the hypothesis earlier in the this paper that peer learning is a major mode of knowledge transfer during hack weeks, and that this type of learning takes place at all career stages. However, we find no strong evidence for a significant difference between early-career researchers and senior participants for any of the three hack weeks for questions regarding learning outcomes of new tools and topics (a), improvements in day-to-day research (b) or overall improvements in science (c) (all statistical results are presented in Table \ref{tab:survey}). Only for GHW we find an indication that early-career researchers agree more strongly that the hack week improved their day-to-day research (p=0.02) with a large effect size of $\phi_c = 0.4$ (following \citet{cohen1988}). 
Similarly, we find no strong indication that late-career researchers self-report a higher level of teaching at hack weeks compared to early-career researchers (d).

One important question regarding hack week outcomes is whether participants from underrepresented groups thrive at these events, or whether their full participation is impeded. Significant differences between minorities and non-minorities, even on a self-reported scale, for questions related to learning outcomes, teaching or network building would indicate that improvements in workshop facilitation and structure may be required to allow participants of all stripes to participate fully.
In Section 4 of the Appendix, we lay out various strategies we have employed to facilitate participation, empower members of underrepresented groups and mitigate impostor syndrome. Based on our surveys, we find no significant dependence of self-reported learning outcomes on gender identity or race/ethnicity (Table \ref{tab:survey}). Similarly, participants who self-identified as minorities with respect to gender identity and race or ethnicity do not significantly differ in their answers with respect to teaching outcomes for any of the hack weeks. Both underrepresented groups similarly feel that they built equally valuable connections at all three hack weeks and generally feel that their contributions to their hack teams were valued. For GHW, there is a weak indication that participants from racial/ethnic minorities respond more positively when asked about building connections (p=0.04) with a medium to large effect size ($\phi_c = 0.4$), while for AHW, responses regarding the value of contributions to hack teams may be spread more widely for participants from racial/ethnic minorities than for Caucasian participants ($p = 0.01; \phi_c = 0.4$). These initial results indicate that future work on how demographics interact with hack week attendance may be fruitful. We note that since we did not include a question about impostor syndrome itself, we cannot draw causal connections between our results and its prevalence. Additionally, our number of respondents is small, and the lack of significant differences may be caused by the small statistical power of our sample.
%It is notable, however, that we find no correlation between the response to this question and career stage for any of the events surveyed here. Participants at all career stages report similar engagement in teaching. This suggests there is some evidence for our hypothesis that compared to e.g.\ a traditional summer school, a hack week is less hierarchical and encourages lateral knowledge transfer between participants at different career stages. However, we note that the sample sizes per category are relatively small, and future work is needed to confirm this hypothesis. We similarly find no correlations with gender identity or race/ethnicity.

We find that the hack weeks have been largely successful at efforts to promote positive attitudes towards reproducibility and open science: at all three events, the majority reports that the hack week has made them more comfortable with open science  (GHW: 97\%; NHW: 95\%; AHW: 72\%, Figure \ref{fig:survey}, (h)). At all three events, more than 85\% of all participants (AHW: 86\%, GHW: 94\%, NHW: 95\%; Figure \ref{fig:survey}, (g) ) put code or data created at the hack week into a public repository.
%The overall behaviour hints at how general conventions and attitudes differ in different fields.
%Astronomy shows the largest degree of openness toward open science, whereas our results indicate that open science is still fairly uncommon in the geosciences, with neuroscience falling in between.
%Similar attitudes are reflected when asking whether the hack week has made participants more comfortable with open science (Figure \ref{fig:survey}, (j)): again, geoscience shows the large improvement with over 97\% agreeing with this statement to some degree, followed by neuroscience (95\%) and astronomy (72\%).
%Overall, our results indicate that hack weeks are effective at addressing persisting doubts about making research open and reproducible. 
While the focus on open science is not necessarily a required component of a hack week, it aligns naturally with many of the goals and values commonly promoted at hack weeks like open-source software and data sharing. In some fields, especially where ethical issues around data sharing and privacy are relevant, this might not be a desired focus of the hack week, or might be replaced or augmented by a discussion of ethical considerations.

We caution the reader that the survey results should be read only as an indication of the hypotheses we proposed about the use and outcomes of hack weeks, in line with the exploratory nature of the surveys conducted as part of the hack weeks. The most important independent variable--attendance at the hack week--is something that our current survey design cannot account for. Moreover, self-reported learning outcomes are not an objective measure, because they are likely subject to internal biases of respondents. While these surveys were largely of an exploratory nature, future work will include more a more refined survey design as well as attendance versus non-attendance as a control variable.

### 2018-04-12 supplementary_material.tex
Additional figures for appendix, added table to results section, modified text

@@

@@

Event size (i.e. the number of attendees) and event duration are important to consider during the design and planning phase of a hack week. All hack weeks held so far have had group sizes between 40-60 participants. The number of attendees resulted from a number of different design considerations. One practical consideration was the size of the available location: especially the project-focused parts of a hack week generally require a reconfigurable space with more seats than attendees, such that spontaneous organization in sub-groups is easy. However, group size is also important in the context of community building, group dynamics and programme decisions. We limited group size to a maximum of 70 participants, because previous anecdotal evidence has shown us that this is about the maximum group size where interactions between all participants is still possible. We wanted to ensure that all participants had an opportunity to at least meet all other participants, in order to facilitate community building and keep the group from fracturing into cliques. Another important consideration is representation along the many axes of diversity we considered. For example, whereas a single undergraduate participant might feel like an outsider, admitting three or four can mitigate alienation. Similarly, in order to foster active collaboration among many different subfields, we endeavored to admit participants with many different types of overlapping expertise. Having a set of participants that is too small would interfere both with these goals of representation and of fostering interdisciplinary collaborations and networking, thus we would advise admitting at least $\sim$30 or so participants if these objectives are an important part of the hack week.

All hack weeks organized up to now have been five days. This duration was chosen to allow enough time for both learning and project work at the same time. Participants often arrived with ambitious project ideas, or with the goal of taking newly learned methods and applying them to their data sets right away. Thus many projects tended to extend over multiple days. Attendees who participated in multiple projects often used the hack week to try out several different ideas. A five-day hack week allows for ample time for these ambitious projects or experimentation, where a shorter hack week would necessarily have to be more constrained and focused. At the same time, hack weeks tend to be exhausting. Project work often extends into the evenings, and requires prolonged phases of high concentration of participants, thus we limited our hack weeks to five days in order to avoid excessive fatigue among our attendees.

@@

Admitting a diverse group of participants is only the first step in encouraging collaboration and knowledge exchange. Community building and careful facilitation of both tutorials and project works are arguably the cornerstones of a successful hack week. This is especially important because the group will inevitably include a wide range of personalities, some of which may find it easier to form new bonds and interact with the group than others. At all hack weeks, we have taken concrete steps to address potential issues and foster a welcoming, inclusive atmosphere. Clearly communicating values and expectations at the beginning for the week can help setting the stage for an environment in which a large range of different personalities can thrive. This includes both communication of the code of conduct, putting an emphasis on collaborative rather than competitive behaviour, as well as a discussion of potential issues participants might experience, such as impostor syndrome (see also section below).

@@

>>>>

\setcounter{tocdepth}{3}

@@

\newpage

\tableofcontents

\newpage

@@

Event size (i.e. the number of attendees) and event duration are important to consider during the design and planning phase of a hack week. All hack weeks we have organized so far have had group sizes between 40-60 participants. The number of attendees resulted from a number of different design considerations. One practical consideration was the size of the available location: especially the project-focused parts of a hack week generally require a reconfigurable space with more seats than attendees, such that spontaneous organization in sub-groups is easy. However, group size is also important in the context of community building, group dynamics and programme decisions. We limited group size to a maximum of 70 participants, because previous anecdotal evidence has shown us that this is about the maximum group size where interactions between all participants is still possible. We wanted to ensure that all participants had an opportunity to at least meet all other participants, in order to facilitate community building and keep the group from fracturing into cliques. Another important consideration is representation along the many axes of diversity we considered. For example, whereas a single undergraduate participant might feel like an outsider, admitting three or four can mitigate alienation. Similarly, in order to foster active collaboration among many different subfields, we endeavored to admit participants with many different types of overlapping expertise. Having a set of participants that is too small would interfere both with these goals of representation and of fostering interdisciplinary collaborations and networking, thus we would advise admitting at least $\sim$30 or so participants if these objectives are an important part of the hack week.

All hack weeks organized by us up to now have been five days. This duration was chosen to allow enough time for both learning and project work at the same time. Participants often arrived with ambitious project ideas, or with the goal of taking newly learned methods and applying them to their data sets right away. Thus many projects tended to extend over multiple days. Attendees who participated in multiple projects often used the hack week to try out several different ideas. A five-day hack week allows for ample time for these ambitious projects or experimentation, where a shorter hack week would necessarily have to be more constrained and focused. At the same time, hack weeks tend to be exhausting. Project work often extends into the evenings, and requires prolonged phases of high concentration of participants, thus we limited our hack weeks to five days in order to avoid excessive fatigue among our attendees.

@@

Admitting a diverse group of participants is only the first step in encouraging collaboration and knowledge exchange. Community building and careful facilitation of both tutorials and project works are arguably the cornerstones of a successful hack week. This is especially important because the group will inevitably include a wide range of personalities, some of which may find it easier to form new bonds and interact with the group than others. At all hack weeks we have organized, we have taken concrete steps to address potential issues and foster a welcoming, inclusive atmosphere. Clearly communicating values and expectations at the beginning for the week can help setting the stage for an environment in which a large range of different personalities can thrive. This includes both communication of the code of conduct, putting an emphasis on collaborative rather than competitive behaviour, as well as a discussion of potential issues participants might experience, such as impostor syndrome (see also section below).

@@

\section{Additional Figures}

Here, we present a number of additional figures related to the survey data presented in the main manuscript. The stacked bar charts presented here allow a closer look at the data that produced the results quoted in Table 1 of the manuscript.

\subsection{Career stage}

Here we explore a number of survey responses with career stage as an independent variable.

\begin{figure*}[h!]
%\begin{center}
%\begin{subfigure}[t]{\textwidth}
\centering
%\caption{}
\includegraphics[width=\textwidth]{Q23_3_Q3_stackedbars.eps}
%\end{subfigure}
\caption{}
\label{fig:survey}
%\end{center}
\end{figure*}

\begin{figure*}[h!]
%\begin{center}
%\begin{subfigure}[t]{\textwidth}
\centering
%\caption{}
\includegraphics[width=\textwidth]{Q24_3_Q3_stackedbars.eps}
%\end{subfigure}
\caption{}
\label{fig:survey}
%\end{center}
\end{figure*}

\begin{figure*}[h!]
%\begin{center}
%\begin{subfigure}[t]{\textwidth}
\centering
%\caption{}
\includegraphics[width=\textwidth]{Q24_4_Q3_stackedbars.eps}
%\end{subfigure}
\caption{}
\label{fig:survey}
%\end{center}
\end{figure*}

\begin{figure*}[h!]
%\begin{center}
%\begin{subfigure}[t]{\textwidth}
\centering
%\caption{}
\includegraphics[width=\textwidth]{Q23_2_Q3_stackedbars.eps}
%\end{subfigure}
\caption{}
\label{fig:survey}
%\end{center}
\end{figure*}

\clearpage

\subsection{Gender Identity}

Here we explore a number of survey responses with gender identity as an independent variable.

\begin{figure*}[h!]
%\begin{center}
%\begin{subfigure}[t]{\textwidth}
\centering
%\caption{}
\includegraphics[width=\textwidth]{Q24_4_Q27_stackedbars.eps}
%\end{subfigure}
\caption{}
\label{fig:survey}
%\end{center}
\end{figure*}

\begin{figure*}[h!]
%\begin{center}
%\begin{subfigure}[t]{\textwidth}
\centering
%\caption{}
\includegraphics[width=\textwidth]{Q23_2_Q27_stackedbars.eps}
%\end{subfigure}
\caption{}
\label{fig:survey}
%\end{center}
\end{figure*}

\begin{figure*}[h!]
%\begin{center}
%\begin{subfigure}[t]{\textwidth}
\centering
%\caption{}
\includegraphics[width=\textwidth]{Q24_5_Q27_stackedbars.eps}
%\end{subfigure}
\caption{}
\label{fig:survey}
%\end{center}
\end{figure*}

\begin{figure*}[h!]
%\begin{center}
%\begin{subfigure}[t]{\textwidth}
\centering
%\caption{}
\includegraphics[width=\textwidth]{Q19_5_Q27_stackedbars.eps}
%\end{subfigure}
\caption{}
\label{fig:survey}
%\end{center}
\end{figure*}

\clearpage

\subsection{Racial/Ethnic Identity}

Here we explore a number of survey responses with racial/ethnic identity as an independent variable.

\begin{figure*}[h!]
%\begin{center}
%\begin{subfigure}[t]{\textwidth}
\centering
%\caption{}
\includegraphics[width=\textwidth]{Q24_4_Q30_stackedbars.eps}
%\end{subfigure}
\caption{}
\label{fig:survey}
%\end{center}
\end{figure*}

\begin{figure*}[h!]
%\begin{center}
%\begin{subfigure}[t]{\textwidth}
\centering
%\caption{}
\includegraphics[width=\textwidth]{Q23_2_Q30_stackedbars.eps}
%\end{subfigure}
\caption{}
\label{fig:survey}
%\end{center}
\end{figure*}

\begin{figure*}[h!]
%\begin{center}
%\begin{subfigure}[t]{\textwidth}
\centering
%\caption{}
\includegraphics[width=\textwidth]{Q24_5_Q30_stackedbars.eps}
%\end{subfigure}
\caption{}
\label{fig:survey}
%\end{center}
\end{figure*}

\begin{figure*}[h!]
%\begin{center}
%\begin{subfigure}[t]{\textwidth}
\centering
%\caption{}
\includegraphics[width=\textwidth]{Q19_5_Q30_stackedbars.eps}
%\end{subfigure}
\caption{}
\label{fig:survey}
%\end{center}
\end{figure*}
